---
title: "Travis Scott Burger Fantasy League 2025"
output: github_document
knit: (function(input, ...) { rmarkdown::render(input, output_file = "README.md", envir = globalenv()) })
---

*All data from [ffscrapr](https://ffscrapr.ffverse.com/){target="_blank"} R library*

___

### Contents

- [Team Standings]
- [Points Scored per Game]
- [Points Against per Game]
- [Points Scored and Against]
- [Optimal Lineup Setting]
- [Season Long Optimal Lineups]
- [Most Points Scored in a Loss]
- [Fewest Points Scored in a Victory]
- [Weekly Scoring Trends]
- [Close Games]
- [Highest Scoring Games]
- [Biggest Blowouts]
- [Closest Games]
- [Most Points Scored by One Team]
- [Fewest Points Scored by One Team]
- [Past Week One Player Merchants]
- [Full Season One Player Merchants]
- [Luckiest Teams This Past Week]
- [Luckiest Teams Season Long]
- [Self Luck and Opponent Luck]
- [Average Weekly Finishing Position]
- [Chug Analysis]
- [Win Percentage by Strength of Schedule]
- [League Wide Optimal Scoring]
- [Top Three Scoring]
- [Bottom Three Scoring]
- [Average Scoring in Wins]
- [Projected Records]
- [Wins When Projected to Lose]
- [Team Records vs League Median]
- [Supreme Luck Merchant]

___

```{r message = F, warning = F, include = F}
library(tidyverse)
library(tvthemes)
library(ffscrapr)
library(ggimage)
library(glue)

theme_custom = theme_avatar() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5, size = 9, vjust = 2.5, face = "italic"),
        plot.caption = element_text(face = "italic"),
        panel.grid.major = element_line(linewidth = 0.5, colour = "#DFDAD1"),
        panel.grid.minor = element_line(linewidth = 0.5, colour = "#DFDAD1"))

theme_set(theme_custom)

conn = ff_connect(platform = "espn", league_id = "81518506", season = 2025)

id_to_name = ff_rosters(conn = conn) |>
  distinct(franchise_id, franchise_name)

team_name_to_name = ff_franchises(conn) |>
  separate(user_name, into = c("first", "last"), sep = " ", remove = T) |>
  select(franchise_name, first)

end_games = ff_schedule(conn, week = 1:14) |>
  filter(franchise_score > 0 & opponent_score > 0) |>
  inner_join(id_to_name, by = "franchise_id") |>
  inner_join(id_to_name, by = c("opponent_id" = "franchise_id")) |>
  rename(franchise_name = franchise_name.x, opponent_name = franchise_name.y) |>
  filter(result == "W") |>
  select(week,
         win_team = franchise_name, win_score = franchise_score,
         lose_score = opponent_score, lose_team = opponent_name)

get_team_total_pts_scored = function(tm) {
  w = end_games |> filter(win_team == tm) |> pull(win_score)
  l = end_games |> filter(lose_team == tm) |> pull(lose_score)
  return(sum(c(w, l)))
}

get_team_total_pts_against = function(tm) {
  w = end_games |> filter(win_team == tm) |> pull(lose_score)
  l = end_games |> filter(lose_team == tm) |> pull(win_score)
  return(sum(c(w, l)))
}

team_records = end_games |>
  count(win_team) |>
  setNames(c("team", "wins")) |>
  full_join(end_games |>
  count(lose_team) |>
  setNames(c("team", "losses")), by = "team") |>
  mutate(wins = coalesce(wins, 0),
         losses = coalesce(losses, 0),
         gp = wins + losses,
         win_pct = round(wins / gp * 100, 2),
         record = paste0(wins, "-", losses)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  mutate(pts_scored = sapply(team, get_team_total_pts_scored),
         pts_against = sapply(team, get_team_total_pts_against)) |>
  arrange(desc(win_pct), desc(pts_scored))

standings_vec = team_records$first
all_teams = sort(unique(c(end_games$win_team, end_games$lose_team)))
```

### Team Standings

```{r echo = F}
team_records |>
  mutate(first = factor(first, levels = rev(standings_vec))) |>
  ggplot(aes(first, win_pct)) +
  geom_col(aes(fill = win_pct), show.legend = F) +
  coord_flip() +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  geom_text(aes(label = record), size = 3, hjust = -0.25) +
  labs(x = NULL, y = NULL,
       title = "2025 Travis Scott Burger Fantasy League Standings",
       caption = "Tiebreaker = total points scored") +
  theme(axis.text.x = element_blank())
```

___

### Points Scored per Game

```{r echo = F}
ymax = max(team_records$pts_scored) / max(end_games$week)

team_records |>
  mutate(ppg = pts_scored / gp) |>
  ggplot(aes(reorder(first, ppg), ppg)) +
  geom_col(aes(fill = ppg), show.legend = F) +
  coord_flip(ylim = c(0, ymax * 1.05)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  geom_text(aes(label = round(ppg, 2)), size = 3, hjust = -0.25) +
  labs(x = NULL, y = NULL,
       title = "Points Scored per Game") +
  theme(axis.text.x = element_blank())
```

___

### Points Against per Game

```{r echo = F}
ymax = max(team_records$pts_against) / max(end_games$week)

team_records |>
  mutate(papg = pts_against / gp) |>
  ggplot(aes(reorder(first, papg), papg)) +
  geom_col(aes(fill = papg), show.legend = F) +
  coord_flip(ylim = c(0, ymax * 1.05)) +
  scale_fill_gradient(low = "springgreen4", high = "indianred3") +
  geom_text(aes(label = round(papg, 2)), size = 3, hjust = -0.25) +
  labs(x = NULL, y = NULL,
       title = "Points Against per Game") +
  theme(axis.text.x = element_blank())
```

___

### Points Scored and Against

```{r echo = F}
team_ppg_papg = team_records |>
  transmute(ppg = pts_scored / gp, papg = pts_against / gp)

team_records |>
  transmute(first, ppg = pts_scored / gp, papg = pts_against / gp, diff = ppg - papg) |>
  ggplot(aes(ppg, papg)) +
  geom_point(aes(col = diff), shape = "square", size = 4, show.legend = F) +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  geom_vline(xintercept = mean(team_ppg_papg$ppg), linetype = "dashed", alpha = 0.5) +
  geom_hline(yintercept = mean(team_ppg_papg$papg), linetype = "dashed", alpha = 0.5) +
  ggrepel::geom_text_repel(aes(label = first), size = 3.5, max.overlaps = 10) +
  labs(x = "Points Scored per Game", y = "Points Against per Game",
       title = "Team points for vs. points against per game",
       subtitle = "Dashed lines represent league averages") +
  scale_x_continuous(breaks = seq(0, 200, by = 5)) +
  scale_y_continuous(breaks = seq(0, 200, by = 5))
```

___

### Optimal Lineup Setting

```{r echo = F}
true_optimal_pts_weekly = espn_potentialpoints(conn, weeks = 1:max(end_games$week)) |>
  distinct(week, franchise_name, franchise_score) |>
  inner_join(espn_potentialpoints(conn, weeks = 1:max(end_games$week)) |>
  filter(!is.na(optimal_slot)) |>
  group_by(week, franchise_name) |>
  summarise(opt = sum(player_score),
            .groups = "drop"), by = c("week", "franchise_name")) |>
  setNames(c("week", "franchise_name", "true_score", "opt_score")) |>
  mutate(missed = round(opt_score - true_score, 2))

vis_data = true_optimal_pts_weekly |>
  filter(week == max(end_games$week)) |>
  inner_join(team_name_to_name, by = "franchise_name") |>
  arrange(missed) |>
  transmute(name = paste0(first, " (", missed, ")"),
            true_score, opt_score)

name_order = vis_data$name

vis_data |>
  mutate(name = factor(name, levels = rev(name_order))) |>
  pivot_longer(!name, names_to = "which", values_to = "pts") |>
  mutate(which = ifelse(which == "opt_score", "Optimal", "Actual")) |>
  ggplot(aes(name, pts)) +
  geom_col(aes(fill = which), position = "dodge") +
  geom_text(aes(label = pts), size = 3, hjust = -0.15, alpha = 0.5,
            position = position_dodge2(width = 0.9)) +
  coord_flip(ylim = c(0, max(vis_data$opt_score) * 1.05)) +
  labs(x = NULL, y = "Points Scored", fill = NULL,
       title = "Who sucked at setting their lineup this past week?",
       subtitle = "Top (best) to bottom (worst)") +
  scale_fill_manual(values = c("indianred3", "springgreen4")) +
  scale_y_continuous(breaks = seq(0, 250, by = 10))
```

___

### Season Long Optimal Lineups

```{r echo = F}
vis_data = true_optimal_pts_weekly |>
  inner_join(team_name_to_name, by = "franchise_name") |>
  group_by(franchise_name) |>
  summarise(true_score = sum(true_score),
            opt_score = sum(opt_score),
            missed = sum(missed)) |>
  inner_join(team_name_to_name, by = "franchise_name") |>
  arrange(missed) |>
  transmute(name = paste0(first, " (", missed, ")"),
            true_score, opt_score)

name_order = vis_data$name

vis_data |>
  mutate(name = factor(name, levels = rev(name_order))) |>
  pivot_longer(!name, names_to = "which", values_to = "pts") |>
  mutate(which = ifelse(which == "opt_score", "Optimal", "Actual")) |>
  ggplot(aes(name, pts)) +
  geom_col(aes(fill = which), position = "dodge") +
  geom_text(aes(label = pts), size = 3, hjust = -0.15, alpha = 0.5,
            position = position_dodge2(width = 0.9)) +
  coord_flip(ylim = c(0, max(vis_data$opt_score) * 1.05)) +
  labs(x = NULL, y = "Points Scored", fill = NULL,
       title = "Who has been the best at setting their lineup this season?",
       subtitle = "Top (best) to bottom (worst)") +
  scale_fill_manual(values = c("indianred3", "springgreen4"))
```

___

### Most Points Scored in a Loss

```{r echo = F}
x = end_games |>
  slice_max(lose_score, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  rename(win_name = first) |>
  inner_join(team_name_to_name, by = c("lose_team" = "franchise_name")) |>
  rename(lose_name = first) |>
  mutate(score = paste0(win_score, "-", lose_score)) |>
  mutate(x = as.character(glue("Week {week}: {win_name} def. {lose_name} {score}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Fewest Points Scored in a Victory

```{r echo = F}
x = end_games |>
  slice_min(win_score, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  rename(win_name = first) |>
  inner_join(team_name_to_name, by = c("lose_team" = "franchise_name")) |>
  rename(lose_name = first) |>
  mutate(score = paste0(win_score, "-", lose_score)) |>
  mutate(x = as.character(glue("Week {week}: {win_name} def. {lose_name} {score}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Weekly Scoring Trends

Coming next week

```{r echo = F}
# end_games |>
#   select(week, team = win_team, score = win_score) |>
#   rbind(end_games |>
#   select(week, team = lose_team, score = lose_score)) |>
#   group_by(team) |>
#   mutate(pct = score / sum(score)) |>
#   ungroup() |>
#   inner_join(team_records |>
#   distinct(team, pts_scored), by = "team") |>
#   inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
#   mutate(first = paste0(first, "\n(", pts_scored, ")")) |>
#   ggplot(aes(week, pct)) +
#   geom_line(aes(col = pts_scored), linewidth = 1.5, show.legend = F) +
#   scale_color_gradient(low = "indianred3", high = "springgreen4") +
#   facet_wrap(vars(first)) +
#   theme(axis.text = element_blank()) +
#   labs(x = "Week", y = "Percent of Total Points Scored",
#        title = "Weekly Scoring Trends",
#        subtitle = "Line color indicates total points scored")
```

___

### Close Games

```{r echo = F}
end_with_margins = end_games |>
  mutate(margin = win_score - lose_score)

get_team_avg_margin = function(tm) {
  x = end_with_margins |> filter(win_team == tm | lose_team == tm) |> pull(margin)
  return(round(mean(x), 2))
}

team_avg_margins = data.frame(team = all_teams) |>
  mutate(avg_margin = sapply(team, get_team_avg_margin)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name"))

team_avg_margins |>
  ggplot(aes(reorder(first, -avg_margin), avg_margin)) +
  geom_col(aes(fill = avg_margin), show.legend = F) +
  coord_flip(ylim = c(0, max(team_avg_margins$avg_margin) * 1.05)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  geom_text(aes(label = avg_margin), size = 3, hjust = -0.25) +
  labs(x = NULL, y = "Average game margin",
       title = "Who is playing the closest games, on average?",
       subtitle = "Without regard to winning or losing") +
  scale_y_continuous(breaks = seq(0, 50, by = 5))
```

___

### Highest Scoring Games

```{r echo = F}
x = end_games |>
  mutate(total = win_score + lose_score,
         final = paste0(win_score, "-", lose_score)) |>
  slice_max(total, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  rename(win_first = first) |>
  inner_join(team_name_to_name, by = c("lose_team" = "franchise_name")) |>
  rename(lose_first = first) |>
  mutate(x = as.character(glue("Week {week}: {win_first} def. {lose_first} {final}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Biggest Blowouts

```{r echo = F}
x = end_games |>
  mutate(score = paste0(win_score, "-", lose_score),
         diff = win_score - lose_score) |>
  slice_max(diff, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  rename(win_name = first) |>
  inner_join(team_name_to_name, by = c("lose_team" = "franchise_name")) |>
  rename(lose_name = first) |>
  mutate(x = as.character(glue("Week {week}: {win_name} def. {lose_name} {score}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Closest Games

```{r echo = F}
x = end_games |>
  mutate(score = paste0(win_score, "-", lose_score),
         diff = win_score - lose_score) |>
  slice_min(diff, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  rename(win_name = first) |>
  inner_join(team_name_to_name, by = c("lose_team" = "franchise_name")) |>
  rename(lose_name = first) |>
  mutate(x = as.character(glue("Week {week}: {win_name} def. {lose_name} {score}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Most Points Scored by One Team

```{r echo = F}
x = end_games |>
  select(week, team = win_team, score = win_score) |>
  rbind(end_games |>
  select(week, team = lose_team, score = lose_score)) |>
  slice_max(score, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  mutate(x = as.character(glue("{score} ({first}, Week {week})"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Fewest Points Scored by One Team

```{r echo = F}
x = end_games |>
  select(week, team = win_team, score = win_score) |>
  rbind(end_games |>
  select(week, team = lose_team, score = lose_score)) |>
  slice_min(score, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  mutate(x = as.character(glue("{score} ({first}, Week {week})"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Past Week One Player Merchants

```{r echo = F}
x = ff_starters(conn, week = max(end_games$week)) |>
  filter(!lineup_slot %in% c("BE", "IR")) |>
  mutate(pct = round(player_score / franchise_score * 100, 1)) |>
  slice_max(pct, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = "franchise_name") |>
  mutate(x = as.character(glue("{player_name}: {pct}% of total points for {first}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Full Season One Player Merchants

```{r echo = F}
x = ff_starters(conn, week = 1:max(end_games$week)) |>
  filter(!lineup_slot %in% c("BE", "IR")) |>
  group_by(franchise_name, player_name) |>
  summarise(pts = sum(player_score),
            .groups = "drop") |>
  inner_join(team_records |>
  select(team, first, pts_scored), by = c("franchise_name" = "team")) |>
  mutate(pct = round(pts / pts_scored * 100, 2)) |>
  slice_max(pct, n = 10, with_ties = F) |>
  mutate(x = as.character(glue("{player_name}: {pct}% of total points for {first}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Luckiest Teams This Past Week

```{r echo = F}
true_proj_scores_weekly = ff_starters(conn, week = 1:max(end_games$week)) |>
  filter(!lineup_slot %in% c("BE", "IR")) |>
  group_by(week, franchise_name) |>
  summarise(true_score = mean(franchise_score),
            proj_score = round(sum(projected_score), 2),
            .groups = "drop")

end_with_proj = end_games |>
  inner_join(true_proj_scores_weekly, by = c("win_team" = "franchise_name", "week")) |>
  rename(win_proj_score = proj_score) |>
  inner_join(true_proj_scores_weekly, by = c("lose_team" = "franchise_name", "week")) |>
  rename(lose_proj_score = proj_score) |>
  select(!contains("true")) |>
  mutate(win_score_over_proj = win_score - win_proj_score,
         lose_score_over_proj = lose_score - lose_proj_score)

past_week_luck_data = end_with_proj |>
  filter(week == max(end_games$week)) |>
  transmute(team = win_team, luck = lose_score_over_proj * -1) |>
  rbind(end_with_proj |>
  filter(week == max(end_games$week)) |>
  transmute(team = lose_team, luck = win_score_over_proj * -1)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  mutate(poslab = ifelse(luck >= 0, round(luck, 1), ""),
         neglab = ifelse(luck < 0, round(luck, 1), ""))

past_week_luck_data |>
  ggplot(aes(reorder(first, luck), luck)) +
  geom_col(aes(fill = luck), show.legend = F) +
  coord_flip(ylim = c(min(past_week_luck_data$luck) * 1.05,
                      max(past_week_luck_data$luck) * 1.05)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  geom_text(aes(label = poslab), size = 3, hjust = -0.25) +
  geom_text(aes(label = neglab), size = 3, hjust = 1.25) +
  labs(x = NULL, y = "Luck",
       title = "Who were the luckiest and unluckiest teams this past week?",
       subtitle = "Opponent-based luck only") +
  theme(axis.text.x = element_blank())
```

___

### Luckiest Teams Season Long

```{r echo = F}
full_szn_luck = end_with_proj |>
  transmute(team = win_team, luck = lose_score_over_proj * -1) |>
  rbind(end_with_proj |>
  transmute(team = lose_team, luck = win_score_over_proj * -1)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  group_by(team, first) |>
  summarise(luck = sum(luck),
            .groups = "drop") |>
  mutate(poslab = ifelse(luck >= 0, round(luck, 1), ""),
         neglab = ifelse(luck < 0, round(luck, 1), ""))

full_szn_luck |>
  ggplot(aes(reorder(first, luck), luck)) +
  geom_col(aes(fill = luck), show.legend = F) +
  coord_flip(ylim = c(min(full_szn_luck$luck) * 1.05,
                      max(full_szn_luck$luck) * 1.05)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  geom_text(aes(label = poslab), size = 3, hjust = -0.25) +
  geom_text(aes(label = neglab), size = 3, hjust = 1.25) +
  labs(x = NULL, y = "Luck",
       title = "Who are the luckiest and unluckiest teams season-long?",
       subtitle = "Opponent-based luck only") +
  theme(axis.text.x = element_blank())
```

___

### Self Luck and Opponent Luck

```{r echo = F}
get_team_score_over_proj = function(tm) {
  w = end_with_proj |> filter(win_team == tm) |> pull(win_score_over_proj)
  l = end_with_proj |> filter(lose_team == tm) |> pull(lose_score_over_proj)
  return(sum(c(w, l)))
}

get_team_opp_score_over_proj = function(tm) {
  w = end_with_proj |> filter(win_team == tm) |> pull(lose_score_over_proj)
  l = end_with_proj |> filter(lose_team == tm) |> pull(win_score_over_proj)
  return(sum(c(w, l ) * -1))
}

data.frame(team = all_teams) |>
  mutate(sop = sapply(team, get_team_score_over_proj),
         luck = sapply(team, get_team_opp_score_over_proj),
         total = sop + luck) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  ggplot(aes(sop, luck)) +
  geom_point(aes(col = total), shape = "square", size = 4, show.legend = F) +
  ggrepel::geom_text_repel(aes(label = first), size = 3.5, max.overlaps = 10) +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(x = "Scoring Over Expected",
       y = "Opponent Scoring Under Expected",
       title = "Who is a ball knower and who is a luck merchant?",
       subtitle = "Unless people request it, this is replacing the 'full luck' stuff") +
  scale_x_continuous(breaks = seq(-250, 250, by = 20)) +
  scale_y_continuous(breaks = seq(-250, 250, by = 20))
```

___

### Average Weekly Finishing Position

```{r echo = F}
pos_data = select(end_games, week, team = win_team, score = win_score) |>
  rbind(select(end_games, week, team = lose_team, score = lose_score)) |>
  group_by(week) |>
  mutate(pos = rank(-score)) |>
  ungroup() |>
  group_by(team) |>
  summarise(avg_pos = round(mean(pos), 2)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name"))

pos_data |>
  ggplot(aes(reorder(first, -avg_pos), avg_pos)) +
  geom_col(aes(fill = avg_pos), show.legend = F) +
  scale_fill_gradient(high = "indianred3", low = "springgreen4") +
  coord_flip(ylim = c(0, max(pos_data$avg_pos) * 1.05)) +
  geom_text(aes(label = avg_pos), size = 3, hjust = -0.25) +
  labs(x = NULL, y = "Average weekly finishing position",
       title = "Average weekly finishing position by team") +
  scale_y_continuous(breaks = seq(0, 10, by = 1))
```

For example: if Hank had the best score in the league, the third best score in the league, and the second best score in the league through three weeks, his average weekly finishing position would be (1 + 3 + 2) / 3 = 2. Closely related to points per game, but not the exact same.

___

### Chug Analysis

Where Adam chug?

```{r echo = F}
# names = c("Josh", "Drew", "Hank", "David", "Josh", "Chad")
# weeks = c(1, 1, 4, 6, 7, 12)
# times = c(29, 13, 10, 9, 27, 16)
# 
# data.frame(name = names, week = weeks, time = times) |>
#   mutate(lab = paste0(name, " (Week ", week, ")"),
#          timelab = paste0(time, "s")) |>
#   ggplot(aes(reorder(lab, -time), time)) +
#   geom_col(fill = "saddlebrown") +
#   coord_flip(ylim = c(0, max(times) * 1.05)) +
#   geom_text(aes(label = timelab), size = 3, hjust = -0.25) +
#   labs(x = NULL, y = NULL,
#        title = "straight chugging it, and by it, let's justr say, well, my bervage") +
#   theme(axis.text.x = element_blank())
```

___

### Win Percentage by Strength of Schedule

```{r echo = F}
get_opp_proj_scores = function(tm) {
  w = end_with_proj |> filter(win_team == tm) |> pull(lose_proj_score)
  l = end_with_proj |> filter(lose_team == tm) |> pull(win_proj_score)
  return(round(mean(c(w, l)), 2))
}

sos_pct_data = data.frame(team = all_teams) |>
  mutate(sos = sapply(team, get_opp_proj_scores)) |>
  inner_join(team_records, by = "team") |>
  mutate(win_pct = win_pct / 100)

sos_pct_data |>
  ggplot(aes(sos, win_pct)) +
  geom_point(aes(col = win_pct), size = 4, shape = "square", show.legend = F) +
  ggrepel::geom_text_repel(aes(label = first), size = 3.5, max.overlaps = 10) +
  geom_line(stat = "smooth", formula = y ~ x, method = "lm", linetype = "dashed") +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  geom_vline(xintercept = mean(sos_pct_data$sos), linetype = "dotted", alpha = 0.5) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.5) +
  labs(x = "Strength of Schedule Rating",
       y = "Win Percentage",
       title = "Win Percentage by Strength of Schedule") +
  scale_x_continuous(breaks = seq(100, 130, by = 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = scales::percent)
```

Strength of schedule is calculated as the average projected score of your opponents. So if JP were to play three opponents with projected scores of 100, 110, and 120, his SOS rating would be (100 + 110 + 120) / 3 = 110.

___

### League Wide Optimal Scoring

Coming next week

```{r echo = F}
# league_week_opt = espn_potentialpoints(conn, weeks = 1:max(end_games$week)) |>
#   filter(!is.na(optimal_slot)) |>
#   group_by(week) |>
#   summarise(score = sum(player_score)) |>
#   inner_join(espn_potentialpoints(conn, weeks = 1:max(end_games$week)) |>
#   distinct(week, franchise_name, franchise_score) |>
#   group_by(week) |>
#   summarise(true = sum(franchise_score)), by = "week") |>
#   mutate(diff = score - true)
# 
# league_week_opt_long = league_week_opt |>
#   pivot_longer(cols = c(score, true), names_to = "which", values_to = "pts") |>
#   mutate(which = ifelse(which == "score", "Optimal", "Actual"))
# 
# midpoints = league_week_opt_long |>
#   pivot_wider(names_from = "which", values_from = "pts") |>
#   mutate(y_mid = (Optimal + Actual) / 2) |>
#   select(week, y_mid, diff)
# 
# league_week_opt_long |>
#   mutate(which = factor(which, levels = c("Optimal", "Actual"))) |>
#   ggplot(aes(week, pts)) +
#   geom_line(aes(col = which), linewidth = 2) +
#   geom_text(data = midpoints, aes(x = week, y = y_mid, label = diff), size = 3.5) +
#   scale_color_manual(values = c("indianred3", "springgreen4")) +
#   labs(x = "Week", y = "Points", col = NULL,
#        title = "League-Wide Optimal vs. True Scoring",
#        subtitle = "Number between lines represents total points missed") +
#   scale_x_continuous(breaks = seq(1, 16, by = 1)) +
#   scale_y_continuous(breaks = seq(750, 1500, by = 50)) +
#   theme(legend.position = "right")
```

___

### Top Three Scoring

```{r echo = F}
ms_ref = select(end_games, week, team = win_team, score = win_score) |>
  rbind(select(end_games, week, team = lose_team, score = lose_score)) |>
  group_by(week) |>
  mutate(rk = rank(-score)) |>
  ungroup() |>
  filter(rk <= 3) |>
  group_by(team) |>
  summarise(ms = mean(score))

select(end_games, week, team = win_team, score = win_score) |>
  rbind(select(end_games, week, team = lose_team, score = lose_score)) |>
  group_by(week) |>
  mutate(rk = rank(-score)) |>
  ungroup() |>
  filter(rk <= 3) |>
  count(team) |>
  arrange(desc(n)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  inner_join(ms_ref, by = "team") |>
  arrange(desc(n), desc(ms)) |>
  mutate(rn = row_number()) |>
  ggplot(aes(reorder(first, -rn), n)) +
  geom_col(fill = "springgreen4") +
  geom_text(aes(label = n), size = 3, hjust = -0.75) +
  coord_flip() +
  labs(x = NULL, y = "Count",
       title = "Most times finishing with a top three score",
       subtitle = "Ties ordered by average score in those games") +
  theme(axis.text.x = element_blank())
```

___

### Bottom Three Scoring

```{r echo = F}
ms_ref = select(end_games, week, team = win_team, score = win_score) |>
  rbind(select(end_games, week, team = lose_team, score = lose_score)) |>
  group_by(week) |>
  mutate(rk = rank(-score)) |>
  ungroup() |>
  filter(rk >= 8) |>
  group_by(team) |>
  summarise(ms = mean(score))

select(end_games, week, team = win_team, score = win_score) |>
  rbind(select(end_games, week, team = lose_team, score = lose_score)) |>
  group_by(week) |>
  mutate(rk = rank(-score)) |>
  ungroup() |>
  filter(rk >= 8) |>
  count(team) |>
  arrange(desc(n)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  inner_join(ms_ref, by = "team") |>
  arrange(desc(n), ms) |>
  mutate(rn = row_number()) |>
  ggplot(aes(reorder(first, -rn), n)) +
  geom_col(fill = "springgreen4") +
  geom_text(aes(label = n), size = 3, hjust = -0.75) +
  coord_flip() +
  labs(x = NULL, y = "Count",
       title = "Most times finishing with a bottom three score",
       subtitle = "Ties ordered by average score in those games") +
  theme(axis.text.x = element_blank())
```

___

### Average Scoring in Wins

```{r echo = F}
end_games |>
  group_by(win_team) |>
  summarise(ws = mean(win_score),
            ls = mean(lose_score)) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  ggplot(aes(ws, ls)) +
  geom_point(aes(col = ws), size = 4, shape = "square", show.legend = F) +
  ggrepel::geom_text_repel(aes(label = first), size = 3, max.overlaps = 10) +
  geom_line(stat = "smooth", method = "lm", formula = y ~ x, linetype = "dashed") +
  labs(x = "Average Score in Wins", y = "Average Opponent Score in Wins",
       title = "Who needs their opponent to stink in order to win?",
       subtitle = "I fear I'm not beating the allegations") +
  scale_x_continuous(breaks = seq(50, 200, by = 5)) +
  scale_y_continuous(breaks = seq(50, 200, by = 5)) +
  scale_color_gradient(low = "indianred3", high = "springgreen4")
```

___

### Projected Records

```{r echo = F}
weekly_proj_wl = end_with_proj |>
  mutate(win_half_score = (win_score + win_proj_score) / 2,
         lose_half_score = (lose_score + lose_proj_score) / 2,
         proj_winner = ifelse(win_proj_score > lose_proj_score, win_team, lose_team),
         proj_loser = ifelse(win_proj_score > lose_proj_score, lose_team, win_team))

team_total_proj = true_proj_scores_weekly |>
  group_by(franchise_name) |>
  summarise(score = sum(proj_score))

proj_plot = weekly_proj_wl |>
  count(proj_winner) |>
  setNames(c("team", "proj_wins")) |>
  full_join(weekly_proj_wl |>
  count(proj_loser) |>
  setNames(c("team", "proj_losses")), by = "team") |>
  mutate(proj_wins = coalesce(proj_wins, 0),
         proj_losses = coalesce(proj_losses, 0),
         win_pct = round(proj_wins / (proj_wins + proj_losses) * 100, 1),
         record = paste0(proj_wins, "-", proj_losses)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  inner_join(team_total_proj, by = c("team" = "franchise_name")) |>
  arrange(desc(win_pct), desc(score))

proj_plot |>
  mutate(first = factor(first, levels = rev(proj_plot$first))) |>
  ggplot(aes(first, win_pct)) +
  geom_col(aes(fill = win_pct), show.legend = F) +
  coord_flip(ylim = c(0, max(proj_plot$win_pct) * 1.05)) +
  geom_text(aes(label = record), size = 3, hjust = -0.25) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  labs(x = NULL, y = NULL,
       title = "Projected Records",
       subtitle = "Tiebreaker = total points scored") +
  theme(axis.text.x = element_blank())
```

___

### Wins When Projected to Lose

```{r echo = F}
x = data.frame(win_team = all_teams) |>
  full_join(end_with_proj |>
  mutate(proj_winner = ifelse(win_proj_score > lose_proj_score, win_team, lose_team),
         upset = ifelse(win_team != proj_winner, 1, 0)) |>
  filter(upset == 1) |>
  count(win_team), by = "win_team") |>
  mutate(n = coalesce(n, 0)) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  mutate(x = ifelse(n != 1, as.character(glue("{first}: {n} wins when projected to lose")),
                    as.character(glue("{first}: {n} win when projected to lose")))) |>
  arrange(desc(n), first) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`
- `r x[6]`
- `r x[7]`
- `r x[8]`
- `r x[9]`
- `r x[10]`

___

### Team Records vs League Median

```{r echo = F}
team_scores_weekly = select(end_games, week, team = win_team, score = win_score) |>
  rbind(select(end_games, week, team = lose_team, score = lose_score))

weekly_median_scores = team_scores_weekly |>
  group_by(week) |>
  summarise(med_score = median(score))

team_records_vs_median = team_scores_weekly |>
  inner_join(weekly_median_scores, by = "week") |>
  mutate(win = ifelse(score > med_score, 1, 0),
         loss = ifelse(score < med_score, 1, 0)) |>
  group_by(team) |>
  summarise(wins = sum(win),
            losses = sum(loss)) |>
  mutate(pct = round(wins / (wins + losses) * 100, 1),
         record = paste0(wins, "-", losses)) |>
  inner_join(team_records |>
  select(team, pts_scored), by = "team") |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  arrange(desc(pct), pts_scored)

team_records_vs_median |>
  mutate(first = factor(first, levels = rev(team_records_vs_median$first))) |>
  ggplot(aes(first, pct)) +
  geom_col(aes(fill = pct), show.legend = F) +
  geom_text(aes(label = record), size = 3, hjust = -0.25) +
  coord_flip(ylim = c(0, max(team_records_vs_median$pct) * 1.05)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  labs(x = NULL, y = NULL,
       title = "Team Records vs. Weekly Median Score",
       caption = "Tiebreaker = total points scored") +
  theme(axis.text.x = element_blank())
```

___

### Supreme Luck Merchant

```{r echo = F}
lucky = data.frame(team = all_teams) |>
  mutate(sop = sapply(team, get_team_score_over_proj),
         luck = sapply(team, get_team_opp_score_over_proj),
         total = sop + luck) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  distinct(first, luck) |>
  inner_join(sos_pct_data |>
  distinct(first, sos), by = "first") |>
  mutate(luck_scaled = scale(luck),
         sos_scaled = scale(sos),
         total = round(luck_scaled - sos_scaled, 3),
         lbl = paste0(first, " (", total, ")"))

lucky |>
  ggplot(aes(sos, luck)) +
  geom_point(aes(col = total), size = 4, shape = "square", show.legend = F) +
  geom_vline(xintercept = mean(lucky$sos), linetype = "dashed", alpha = 0.5) +
  geom_hline(yintercept = mean(lucky$luck), linetype = "dashed", alpha = 0.5) +
  ggrepel::geom_text_repel(aes(label = lbl), size = 3) +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  labs(x = "Strength of Schedule (Avg. Opponent Proj. Score)",
       y = "Luck (Total Opponent Scoring Under Expected",
       title = "Who is the supreme luck merchant?",
       subtitle = "Note the x-axis is flipped so top-right is the 'luckiest' quadrant") +
  scale_x_reverse(breaks = seq(100, 125, by = 1)) +
  scale_y_continuous(breaks = seq(-125, 125, by = 25))
```

**Label numbers explained**: To calculate these overall values, I normalized both everyone's strength of schedule ratings and their luck ratings so that they are on the same scale. Note that my calculation assumes these two are equal, i.e. strength of schedule and opponent scoring under average play an equal role in determining someone's "luck" as we're loosely defining it. Once I have these two normalized numbers, I subtract the normalized SOS score from the normalized luck score because a lower SOS is "luckier" so to speak. This then determines the overall number you see in parentheses next to everyone's names.

___
































