---
title: "Travis Scott Burger Fantasy League 2025"
output: github_document
knit: (function(input, ...) { rmarkdown::render(input, output_file = "README.md", envir = globalenv()) })
---

### Contents

- [Team Standings]
- [Points Scored Per Game]
- [Points Against Per Game]
- [Scatterplot of Points Scored and Against]
- [Optimal Lineup Setting]
- [Season-Long Optimal Lineups]
- [Most Points Scored in a Loss]
- [Fewest Points Scored in a Victory]
- [Weekly Scoring Trends]
- [Close Games]
- [Highest Scoring Games]
- [Biggest Blowouts]
- [Closest Games]
- [Most Points Scored by One Team]
- [Fewest Points Scored by One Team]
- [Past Week One Player Merchants]
- [Full Season One Player Merchants]
- [Luckiest Teams This Past Week]
- [Luckiest Teams Season Long]
- [Past Week Full Luck]
- [Season Long Full Luck]
- [Average Weekly Finishing Position]
- [Chug Analysis]


```{r message = F, warning = F, echo = F}
library(tidyverse)
library(tvthemes)
library(googlesheets4)
library(ggimage)
library(glue)

theme_custom = theme_avatar() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5, size = 9, vjust = 2.5, face = "italic"),
        plot.caption = element_text(face = "italic"),
        panel.grid.major = element_line(linewidth = 0.5, colour = "#DFDAD1"),
        panel.grid.minor = element_line(linewidth = 0.5, colour = "#DFDAD1"))

theme_set(theme_custom)
gs4_auth(email = "chadallison1251@gmail.com")
base = "https://docs.google.com/spreadsheets/"
rest = "d/1YCOgxROEPzAnqchVIXemAZ0av5sjVvIroeM9KZNIBkw/edit?usp=sharing"
url = paste0(base, rest)
teams = read_sheet(url, sheet = 1)
games = read_sheet(url, sheet = 2)
opt = read_sheet(url, sheet = 3)
draft = read_sheet(url, sheet = 4)
chug = read_sheet(url, sheet = 5)

end_games = games |>
  filter(!is.na(away_score) & !is.na(home_score)) |>
  mutate(win_team = ifelse(home_score > away_score, home_team, away_team),
         win_score = ifelse(home_score > away_score, home_score, away_score),
         lose_team = ifelse(home_score > away_score, away_team, home_team),
         lose_score = ifelse(home_score > away_score, away_score, home_score))

all_teams = sort(unique(c(unique(end_games$home_team), unique(end_games$away_team))))
```

___

### Team Standings

```{r echo = F}
team_records = data.frame(team = all_teams) |>
  left_join(teams, by = c("team" = "team_name")) |>
  separate(manager, into = c("manager", "last"), sep = " ") |>
  select(team, manager) |>
  left_join(end_games |>
  count(win_team) |>
  rename(team = win_team, wins = n), by = "team") |>
  left_join(end_games |>
  count(lose_team) |>
  rename(team = lose_team, losses = n), by = "team") |>
  mutate(wins = replace_na(wins, 0),
         losses = replace_na(losses, 0),
         record = paste0(wins, "-", losses),
         pct = round(wins / (wins + losses), 3),
         team_name = team)

get_pts_scored = function(team) {
  home = end_games |> filter(home_team == team) |> pull(home_score)
  away = end_games |> filter(away_team == team) |> pull(away_score)
  return(mean(c(home, away)))
}

pts_scored = data.frame(team = all_teams) |>
  mutate(scored = sapply(team, get_pts_scored))

standings_order = team_records |>
  inner_join(distinct(pts_scored, team, scored), by = "team") |>
  arrange(desc(pct), desc(scored)) |>
  pull(team_name)

team_records |>
  mutate(team_name = factor(team_name, levels = rev(standings_order))) |>
  ggplot(aes(team_name, pct)) +
  geom_col(fill = "#90AC8D") +
  geom_text(aes(label = record), size = 3, hjust = -0.25) +
  coord_flip(ylim = c(0, max(team_records$pct * 1.05))) +
  labs(x = NULL, y = "Win Percentage",
       title = "Team Standings") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = scales::percent)
```

___

### Points Scored Per Game

```{r echo = F}
pts_scored |>
  ggplot(aes(reorder(team, scored), scored)) +
  geom_col(aes(fill = scored), show.legend = F) +
  geom_text(aes(label = round(scored, 2)), size = 3, hjust = -0.25) +
  coord_flip(ylim = c(0, max(pts_scored$scored * 1.05))) +
  scale_fill_gradient(high = "#82B47D", low = "#CF9696") +
  scale_y_continuous(breaks = seq(0, 150, by = 10)) +
  labs(x = NULL, y = "Points Scored Per Game",
       title = "Points Scored Per Game Standings")
```

___

### Points Against Per Game

```{r echo = F}
get_pts_against = function(team) {
  home = end_games |> filter(home_team == team) |> pull(away_score)
  away = end_games |> filter(away_team == team) |> pull(home_score)
  return(mean(c(home, away)))
}

pts_against = data.frame(team = all_teams) |>
  mutate(against = sapply(team, get_pts_against))

pts_against |>
  ggplot(aes(reorder(team, against), against)) +
  geom_col(aes(fill = against), show.legend = F) +
  geom_text(aes(label = round(against, 2)), size = 3, hjust = -0.25) +
  coord_flip(ylim = c(0, max(pts_against$against * 1.05))) +
  scale_fill_gradient(low = "#82B47D", high = "#CF9696") +
  scale_y_continuous(breaks = seq(0, 150, by = 10)) +
  labs(x = NULL, y = "Points Against Per Game",
       title = "Points Against Per Game Standings")
```

___

### Scatterplot of Points Scored and Against

```{r echo = F}
scored_against = data.frame(team = all_teams) |>
  mutate(scored = sapply(team, get_pts_scored),
         against = sapply(team, get_pts_against)) |>
  mutate(diff = scored - against)

scored_against |>
  ggplot(aes(scored, against)) +
  geom_point(aes(col = diff), shape = "square", size = 5, show.legend = F) +
  ggrepel::geom_text_repel(aes(label = team), size = 3, box.padding = 0.5, segment.alpha = 0) +
  geom_hline(yintercept = mean(scored_against$against), linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = mean(scored_against$scored), linetype = "dashed", alpha = 0.5) +
  scale_color_gradient(low = "#CF9696", high = "#82B47D") +
  scale_x_continuous(breaks = seq(0, 200, by = 5)) +
  scale_y_continuous(breaks = seq(0, 200, by = 5)) +
  labs(x = "Points Scored", y = "Points Against",
       title = "Scatterplot of Points Scored v. Against",
       subtitle = "Dashed Lines Represent League Averages")
```

___

### Optimal Lineup Setting

```{r message = F, warning = F, echo = F}
get_score = function(team, wk) {
  # print(sprintf("team: %s, week: %s", team, wk))
  df = end_games |> filter(week == wk & (away_team == team | home_team == team))
  if (df$home_team == team) return(df$home_score)
  if (df$away_team == team) return(df$away_score)
}

get_optimal_score = function(team, wk) {
  df = opt |> filter(team_name == team & week == wk) |> mutate(used = 0, pnum = row_number())
  all_pos = unique(df$pos)
  for (i in 1:length(all_pos)) if (!all_pos[i] %in% c("dst", "k", "qb", "rb", "te", "wr")) return(warning("Ensure positions entered correctly"))
  qb1 = df |> filter(pos == "qb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  qb1n = df |> filter(pos == "qb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == qb1n, 1, 0))
  qb2 = df |> filter(pos == "qb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  qb2n = df |> filter(pos == "qb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == qb2n, 1, 0))
  rb1 = df |> filter(pos == "rb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  rbn1 = df |> filter(pos == "rb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == rbn1, 1, 0))
  rb2 = df |> filter(pos == "rb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  rbn2 = df |> filter(pos == "rb" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == rbn2, 1, 0))
  wrte1 = df |> filter(pos %in% c("wr", "te") & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  wrten1 = df |> filter(pos %in% c("wr", "te") & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == wrten1, 1, 0))
  wrte2 = df |> filter(pos %in% c("wr", "te") & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  wrten2 = df |> filter(pos %in% c("wr", "te") & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == wrten2, 1, 0))
  x1 = df |> filter(pos %in% c("rb", "wr", "te") & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  x1n = df |> filter(pos %in% c("rb", "wr", "te") & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == x1n, 1, 0))
  dst = df |> filter(pos == "dst" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  dstn = df |> filter(pos == "dst" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == dstn, 1, 0))
  k = df |> filter(pos == "k" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pts)
  kn = df |> filter(pos == "k" & used == 0) |> slice_max(pts, n = 1, with_ties = F) |> pull(pnum)
  df = df |> mutate(used = ifelse(used == 1 | pnum == kn, 1, 0))
  return(qb1 + qb2 + rb1 + rb2 + wrte1 + wrte2 + x1 + dst + k)
}

teams_vec = rep(all_teams, times = max(end_games$week))
week_vec = NULL

for (i in 1:max(end_games$week)) {
  new_vec = rep(i, times = 10)
  week_vec = c(week_vec, new_vec)
}

optimal_df = data.frame(team = teams_vec, week = week_vec) |>
  rowwise() |>
  mutate(actual_pts = get_score(team, week),
         optimal_pts = get_optimal_score(team, week)) |>
  ungroup() |>
  mutate(missed_pts = optimal_pts - actual_pts) |>
  pivot_longer(!c(team, week, missed_pts), names_to = "class", values_to = "value") |>
  mutate(team = paste0(team, " (", round(missed_pts, 3), ")"),
         class = ifelse(class == "actual_pts", "Actual", "Optimal"))

max_week = max(optimal_df$week)

optimal_df |>
  filter(week == max_week) |>
  ggplot(aes(reorder(team, -missed_pts), value)) +
  geom_col(aes(fill = class), position = "dodge") +
  geom_text(aes(label = value), size = 3, position = position_dodge2(width = 0.9), hjust = -0.15, alpha = 0.5) +
  coord_flip(ylim = c(0, max(optimal_df$value) * 1.05)) +
  labs(x = NULL, y = "Points Scored", fill = NULL,
       title = "Who sucked at setting their lineup this past week?",
       subtitle = "Top (best) to bottom (worst)") +
  scale_fill_manual(values = c("#CF9696", "#82B47D")) +
  scale_y_continuous(breaks = seq(0, 1000, by = 10))
```

___

### Season-Long Optimal Lineups

```{r echo = F}
szn_optimal = data.frame(team = teams_vec, week = week_vec) |>
  rowwise() |>
  mutate(actual_pts = get_score(team, week),
         optimal_pts = get_optimal_score(team, week)) |>
  ungroup() |>
  group_by(team) |>
  summarise(actual_pts = sum(actual_pts),
            optimal_pts = sum(optimal_pts)) |>
  mutate(missed_pts = optimal_pts - actual_pts) |>
  pivot_longer(c(actual_pts, optimal_pts), names_to = "class", values_to = "value") |>
  mutate(class = ifelse(class == "actual_pts", "Actual", "Optimal"),
         team = paste0(team, " (", round(missed_pts, 2), ")"))

szn_optimal |>
  ggplot(aes(reorder(team, -missed_pts), value)) +
  geom_col(aes(fill = class), position = "dodge") +
  geom_text(aes(label = value), size = 3, position = position_dodge2(width = 0.9), hjust = -0.15, alpha = 0.5) +
  coord_flip(ylim = c(0, max(szn_optimal$value) * 1.05)) +
  labs(x = NULL, y = "Points Scored", fill = NULL,
       title = "Who is the best at setting their lineup this season?",
       subtitle = "Top (best) to bottom (worst)") +
  scale_fill_manual(values = c("#CF9696", "#82B47D"))
```

___


### Most Points Scored in a Loss

```{r echo = F}
desc = end_games |>
  select(week, win_team, lose_team, win_score, lose_score) |>
  slice_max(lose_score, n = 5, with_ties = F) |>
  mutate(desc = paste0("Week ", week, ": ", win_team, " def. ", lose_team, " ", win_score, "-", lose_score)) |>
  pull(desc)
```

- `r desc[1]`
- `r desc[2]`
- `r desc[3]`
- `r desc[4]`
- `r desc[5]`

___

### Fewest Points Scored in a Victory

```{r echo = F}
desc = end_games |>
  select(week, win_team, lose_team, win_score, lose_score) |>
  slice_min(win_score, n = 5, with_ties = F) |>
  mutate(desc = paste0("Week ", week, ": ", win_team, " def. ", lose_team, " ", win_score, "-", lose_score)) |>
  pull(desc)
```

- `r desc[1]`
- `r desc[2]`
- `r desc[3]`
- `r desc[4]`
- `r desc[5]`

___

### Weekly Scoring Trends

```{r echo = F}
get_total_pts_scored = function(team) {
  home = end_games |> filter(home_team == team) |> pull(home_score) |> sum()
  away = end_games |> filter(away_team == team) |> pull(away_score) |> sum()
  return(home + away)
}

weekly_scores = data.frame()

for (i in 1:length(all_teams)) {
  for (j in 1:max(end_games$week)) {
    df = end_games |> filter(week == j & (home_team == all_teams[i] | away_team == all_teams[i]))
    if (nrow(df) == 0) next
    if (df$home_team == all_teams[i]) value = df$home_score
    if (df$away_team == all_teams[i]) value = df$away_score
    x = data.frame(team = all_teams[i], week = j, score = value)
    weekly_scores = rbind(weekly_scores, x)
  }
}

weekly_scores |>
  mutate(total_score = sapply(team, get_total_pts_scored),
         week_pct = round(score / total_score, 3),
         team = paste0(team, "\n(", total_score, ")")) |>
  ggplot(aes(week, week_pct)) +
  geom_line(aes(col = total_score), linewidth = 2, show.legend = F) +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  facet_wrap(vars(team)) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Week Number", y = "Percent of Total Points Scored",
       title = "Weekly Scoring Trends",
       subtitle = "Line Color Indicates Total Points Scored")
```

___

### Close Games

```{r echo = F}
end_margins = end_games |>
  mutate(game_margin = abs(home_score - away_score))

get_team_avg_margin = function(team) {
  return(end_margins |>
    filter(home_team == team | away_team == team) |>
    pull(game_margin) |>
    mean() |>
    round(2))
}

margin_vis_df = data.frame(team = all_teams) |>
  mutate(avg_margin = sapply(team, get_team_avg_margin))

margin_vis_df |>
  ggplot(aes(reorder(team, -avg_margin), avg_margin)) +
  geom_col(aes(fill = avg_margin), show.legend = F) +
  geom_text(aes(label = avg_margin), size = 3.5, hjust = -0.25) +
  coord_flip(ylim = c(0, max(margin_vis_df$avg_margin) * 1.1)) +
  scale_fill_gradient(high = "springgreen4", low = "indianred3") +
  scale_y_continuous(breaks = seq(0, 100, by = 5)) +
  labs(x = NULL, y = "Average Game Margin",
       title = "Who is playing the closest games, on average?",
       subtitle = "Without regard to winning or losing")
```

___

### Highest Scoring Games

```{r echo = F}
high = end_games |>
  mutate(total_score = win_score + lose_score,
         x = paste0("Week ", week, ": ", win_team, " def. ", lose_team, " ", win_score, " to ", lose_score)) |>
  slice_max(total_score, n = 5, with_ties = F) |>
  pull(x)
```

- `r high[1]`
- `r high[2]`
- `r high[3]`
- `r high[4]`
- `r high[5]`

___

### Biggest Blowouts

```{r echo = F}
blow = end_games |>
  mutate(margin = abs(win_score - lose_score),
         x = paste0("Week ", week, ": ", win_team, " def. ", lose_team, " ", win_score, " to ", lose_score)) |>
  slice_max(margin, n = 5, with_ties = F) |>
  pull(x)
```

- `r blow[1]`
- `r blow[2]`
- `r blow[3]`
- `r blow[4]`
- `r blow[5]`

___

### Closest Games

```{r echo = F}
close = end_games |>
  mutate(margin = abs(win_score - lose_score),
         x = paste0("Week ", week, ": ", win_team, " def. ", lose_team, " ", win_score, " to ", lose_score)) |>
  slice_min(margin, n = 5, with_ties = F) |>
  pull(x)
```

- `r close[1]`
- `r close[2]`
- `r close[3]`
- `r close[4]`
- `r close[5]`

___

### Most Points Scored by One Team

```{r echo = F}
most = weekly_scores |>
  slice_max(score, n = 5, with_ties = F) |>
  mutate(x = paste0(score, " (", team, ", Week ", week, ")")) |>
  pull(x)
```

- `r most[1]`
- `r most[2]`
- `r most[3]`
- `r most[4]`
- `r most[5]`

___

### Fewest Points Scored by One Team

```{r echo = F}
few = weekly_scores |>
  slice_min(score, n = 5, with_ties = F) |>
  mutate(x = paste0(score, " (", team, ", Week ", week, ")")) |>
  pull(x)
```

- `r few[1]`
- `r few[2]`
- `r few[3]`
- `r few[4]`
- `r few[5]`

___

### Past Week One Player Merchants

```{r echo = F}
x = opt |>
  filter(week == max(end_games$week)) |>
  group_by(team_name, week) |>
  mutate(rn = row_number()) |>
  filter(rn <= 9) |>
  group_by(team_name, week) |>
  mutate(pct = round(pts / sum(pts) * 100, 1),
         pctx = paste0(pct, "%")) |>
  ungroup() |>
  mutate(player = str_remove_all(player, "\n.*"),
         x = paste0(player, ": ", pctx, " of total points for ", team_name)) |>
  slice_max(pct, n = 5, with_ties = F) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`

___

### Full Season One Player Merchants

```{r echo = F}
team_total_pts = opt |>
  group_by(team_name, week) |>
  mutate(rn = row_number()) |>
  filter(rn <= 9) |>
  ungroup() |>
  group_by(team_name) |>
  summarise(total_pts = sum(pts))

player_total_pts = opt |>
  group_by(team_name, week) |>
  mutate(rn = row_number()) |>
  filter(rn <= 9) |>
  ungroup() |>
  group_by(team_name, player) |>
  summarise(pts = sum(pts),
            .groups = "drop")

full_szn_opms = player_total_pts |>
  inner_join(team_total_pts, by = "team_name") |>
  mutate(pct = round(pts / total_pts * 100, 2)) |>
  slice_max(pct, n = 10, with_ties = F) |>
  mutate(player = str_remove_all(player, "\n.*"),
         x = paste0(player, ": ", pct, "% of total points for ", team_name)) |>
  pull(x)
```

1. `r full_szn_opms[1]`
2. `r full_szn_opms[2]`
3. `r full_szn_opms[3]`
4. `r full_szn_opms[4]`
5. `r full_szn_opms[5]`
6. `r full_szn_opms[6]`
7. `r full_szn_opms[7]`
8. `r full_szn_opms[8]`
9. `r full_szn_opms[9]`
10. `r full_szn_opms[10]`

___

### Luckiest Teams This Past Week

```{r echo = F}
team_pts_scored = end_games |>
  group_by(team = home_team) |>
  summarise(home_pts = sum(home_score)) |>
  full_join(end_games |>
  group_by(team = away_team) |>
  summarise(away_pts = sum(away_score)), by = "team") |>
  mutate(home_pts = coalesce(home_pts, 0),
         away_pts = coalesce(away_pts, 0)) |>
  transmute(team, pts = (home_pts + away_pts) / max(end_games$week))

end_luck = end_games |>
  inner_join(team_pts_scored, by = c("home_team" = "team")) |>
  rename(home_ppg = pts) |>
  inner_join(team_pts_scored, by = c("away_team" = "team")) |>
  rename(away_ppg = pts) |>
  mutate(home_luck = away_ppg - away_score,
         away_luck = home_ppg - home_score)

get_team_last_week_luck = function(tm) {
  luck = end_luck |>
    filter(week == max(end_games$week) & (home_team == tm | away_team == tm)) |>
    mutate(my_luck = ifelse(home_team == tm, home_luck, away_luck)) |>
    pull(my_luck)
  
  return(luck)
}

get_team_ovr_luck = function(tm) {
  luck = end_luck |>
    filter(home_team == tm | away_team == tm) |>
    mutate(my_luck = ifelse(home_team == tm, home_luck, away_luck)) |>
    summarise(luck = sum(my_luck)) |>
    pull(luck)
  
  return(luck)
}

luckplot = data.frame(team = all_teams, week = max(end_games$week)) |>
  mutate(luck = sapply(team, get_team_last_week_luck),
         poslab = ifelse(luck >= 0, round(luck, 1), ""),
         neglab = ifelse(luck < 0, round(luck, 1), ""))

luckplot |>
  ggplot(aes(reorder(team, luck), luck)) +
  geom_col(aes(fill = luck), show.legend = F) +
  geom_text(aes(label = poslab), size = 3, hjust = -0.25) +
  geom_text(aes(label = neglab), size = 3, hjust = 1.25) +
  coord_flip(ylim = c(min(luckplot$luck) * 1.1, max(luckplot$luck) * 1.1)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  labs(x = NULL, y = "Luck",
       title = "Who were the luckiest and unluckiest teams this past week?")
```

___

### Luckiest Teams Season Long

```{r echo = F}
luckplot = data.frame(team = all_teams) |>
  mutate(luck = sapply(team, get_team_ovr_luck),
         poslab = ifelse(luck >= 0, round(luck, 1), ""),
         neglab = ifelse(luck < 0, round(luck, 1), ""))

luckplot |>
  ggplot(aes(reorder(team, luck), luck)) +
  geom_col(aes(fill = luck), show.legend = F) +
  geom_text(aes(label = poslab), size = 3, hjust = -0.25) +
  geom_text(aes(label = neglab), size = 3, hjust = 1.25) +
  coord_flip(ylim = c(min(luckplot$luck) * 1.1, max(luckplot$luck) * 1.1)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  labs(x = NULL, y = "Luck",
       title = "Who are the luckiest and unluckiest teams season-long?")
```

___

### Past Week Full Luck

```{r echo = F}
end_luck_full = end_luck |>
  mutate(home_self_luck = (home_score - home_ppg) * 1, # changed factor to 1
         away_self_luck = (away_score - away_ppg) * 1,
         home_full_luck = home_luck + home_self_luck,
         away_full_luck = away_luck + away_self_luck)

get_team_pw_full_luck = function(tm) {
  home = end_luck_full |> filter(week == max(end_games$week) & home_team == tm) |> pull(home_full_luck)
  away = end_luck_full |> filter(week == max(end_games$week) & away_team == tm) |> pull(away_full_luck)
  return(round(sum(c(home, away)), 2))
}

get_team_full_luck = function(tm) {
  home = end_luck_full |> filter(home_team == tm) |> pull(home_full_luck)
  away = end_luck_full |> filter(away_team == tm) |> pull(away_full_luck)
  return(round(sum(c(home, away)), 2))
}

past_week_full_luck = data.frame(team = all_teams) |>
  mutate(pw_luck = sapply(team, get_team_pw_full_luck))

ovr_full_luck = data.frame(team = all_teams) |>
  mutate(luck = sapply(team, get_team_full_luck))

past_week_full_luck |>
  mutate(poslab = ifelse(pw_luck >= 0, pw_luck, ""),
         neglab = ifelse(pw_luck < 0, pw_luck, "")) |>
  ggplot(aes(reorder(team, pw_luck), pw_luck)) +
  geom_col(aes(fill = pw_luck), show.legend = F) +
  geom_text(aes(label = poslab), size = 3, hjust = -0.25) +
  geom_text(aes(label = neglab), size = 3, hjust = 1.25) +
  coord_flip(ylim = c(min(past_week_full_luck$pw_luck) * 1.1, max(past_week_full_luck$pw_luck) * 1.1)) +
  labs(x = NULL, y = "Full Luck",
       title = "Luckiest teams, this past week",
       subtitle = "Full luck, not just opponent luck") +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  scale_y_continuous(breaks = seq(-50, 50, by = 5))
```

___

### Season Long Full Luck

```{r echo = F}
ovr_full_luck |>
  mutate(poslab = ifelse(luck >= 0, luck, ""),
         neglab = ifelse(luck < 0, luck, "")) |>
  ggplot(aes(reorder(team, luck), luck)) +
  geom_col(aes(fill = luck), show.legend = F) +
  geom_text(aes(label = poslab), size = 3, hjust = -0.25) +
  geom_text(aes(label = neglab), size = 3, hjust = 1.25) +
  coord_flip(ylim = c(min(ovr_full_luck$luck) * 1.1, max(ovr_full_luck$luck) * 1.1)) +
  labs(x = NULL, y = "Full Luck",
       title = "Luckiest teams, season long",
       subtitle = "Full luck, not just opponent luck") +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  scale_y_continuous(breaks = seq(-100, 100, by = 10))
```

___

### Average Weekly Finishing Position

```{r echo = F}
end_games |>
  distinct(week, team = home_team, score = home_score) |>
  rbind(end_games |>
  distinct(week, team = away_team, score = away_score)) |>
  group_by(week) |>
  mutate(wk_rank = rank(-score)) |>
  ungroup() |>
  group_by(team) |>
  summarise(avg_rank = round(mean(wk_rank), 2)) |>
  ggplot(aes(reorder(team, -avg_rank), avg_rank)) +
  geom_col(aes(fill = avg_rank), show.legend = F) +
  coord_flip() +
  labs(x = NULL, y = "Average Weekly Finishing Position",
       title = "Average weekly finishing position by team") +
  scale_fill_gradient(high = "indianred3", low = "springgreen4") +
  geom_text(aes(label = avg_rank), size = 3, hjust = -0.25) +
  scale_y_continuous(breaks = seq(0, 10, by = 1))
```

For example: if Hank had the best score in the league, the third best score in the league, and the second best score in the league through three weeks, his average weekly finishing position would be (1 + 3 + 2) / 3 = 2. Closely related to points per game, but not the exact same.

___

### Chug Analysis

```{r echo = F}
chug |>
  mutate(xvar = paste0(manager, " (", week, ")")) |>
  ggplot(aes(reorder(xvar, -time), time)) +
  geom_col(fill = "saddlebrown") +
  geom_text(aes(label = paste0(time, "s")), size = 3, hjust = -0.25) +
  coord_flip() +
  labs(x = NULL, y = NULL,
       title = "straight chugging it, and by it, let's justr say, well, my bervage") +
  theme(axis.text.x = element_blank())
```

# EVERYTHING FROM THIS POINT FORWARD IS A WORK IN PROGRESS


```{r message = F, warning = F}
library(tidyverse)
library(ffscrapr)

conn = ff_connect(platform = "espn", league_id = "81518506", season = 2024)

id_to_name = ff_rosters(conn = conn) |>
  distinct(franchise_id, franchise_name)

team_name_to_name = ff_franchises(conn) |>
  separate(user_name, into = c("first", "last"), sep = " ", remove = T) |>
  select(franchise_name, first)

end_games = ff_schedule(conn, week = 1:14) |>
  filter(franchise_score > 0 & opponent_score > 0) |>
  inner_join(id_to_name, by = "franchise_id") |>
  inner_join(id_to_name, by = c("opponent_id" = "franchise_id")) |>
  rename(franchise_name = franchise_name.x, opponent_name = franchise_name.y) |>
  filter(result == "W") |>
  select(week,
         win_team = franchise_name, win_score = franchise_score,
         lose_score = opponent_score, lose_team = opponent_name)

get_team_total_pts_scored = function(tm) {
  w = end_games |> filter(win_team == tm) |> pull(win_score)
  l = end_games |> filter(lose_team == tm) |> pull(lose_score)
  return(sum(c(w, l)))
}

get_team_total_pts_against = function(tm) {
  w = end_games |> filter(win_team == tm) |> pull(lose_score)
  l = end_games |> filter(lose_team == tm) |> pull(win_score)
  return(sum(c(w, l)))
}

team_records = end_games |>
  count(win_team) |>
  setNames(c("team", "wins")) |>
  full_join(end_games |>
  count(lose_team) |>
  setNames(c("team", "losses")), by = "team") |>
  mutate(wins = coalesce(wins, 0),
         losses = coalesce(losses, 0),
         gp = wins + losses,
         win_pct = round(wins / gp * 100, 2),
         record = paste0(wins, "-", losses)) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  mutate(pts_scored = sapply(team, get_team_total_pts_scored),
         pts_against = sapply(team, get_team_total_pts_against)) |>
  arrange(desc(win_pct), desc(pts_scored))

standings_vec = team_records$first

all_teams = sort(unique(c(end_games$win_team, end_games$lose_team)))
```

### Team Standings v2

```{r}
team_records |>
  mutate(first = factor(first, levels = rev(standings_vec))) |>
  ggplot(aes(first, win_pct)) +
  geom_col(aes(fill = win_pct), show.legend = F) +
  coord_flip() +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  geom_text(aes(label = record), size = 3, hjust = -0.25) +
  labs(x = NULL, y = NULL,
       title = "2024 Travis Scott Burger Fantasy League Standings",
       caption = "Tiebreaker = total points scored") +
  theme(axis.text.x = element_blank())
```

### Points Scored per Game v2

```{r}
ymax = max(team_records$pts_scored) / max(end_games$week)

team_records |>
  mutate(ppg = pts_scored / gp) |>
  ggplot(aes(reorder(first, ppg), ppg)) +
  geom_col(aes(fill = ppg), show.legend = F) +
  coord_flip(ylim = c(0, ymax * 1.05)) +
  scale_fill_gradient(low = "indianred3", high = "springgreen4") +
  geom_text(aes(label = round(ppg, 2)), size = 3, hjust = -0.25) +
  labs(x = NULL, y = NULL,
       title = "Points Scored per Game") +
  theme(axis.text.x = element_blank())
```

### Points Against per Game v2

```{r}
ymax = max(team_records$pts_against) / max(end_games$week)

team_records |>
  mutate(papg = pts_against / gp) |>
  ggplot(aes(reorder(first, papg), papg)) +
  geom_col(aes(fill = papg), show.legend = F) +
  coord_flip(ylim = c(0, ymax * 1.05)) +
  scale_fill_gradient(low = "springgreen4", high = "indianred3") +
  geom_text(aes(label = round(papg, 2)), size = 3, hjust = -0.25) +
  labs(x = NULL, y = NULL,
       title = "Points Against per Game") +
  theme(axis.text.x = element_blank())
```



### Points Scored and Against v2

```{r}
team_ppg_papg = team_records |>
  transmute(ppg = pts_scored / gp, papg = pts_against / gp)

team_records |>
  transmute(first, ppg = pts_scored / gp, papg = pts_against / gp, diff = ppg - papg) |>
  ggplot(aes(ppg, papg)) +
  geom_point(aes(col = diff), shape = "square", size = 4, show.legend = F) +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  geom_vline(xintercept = mean(team_ppg_papg$ppg), linetype = "dashed", alpha = 0.5) +
  geom_hline(yintercept = mean(team_ppg_papg$papg), linetype = "dashed", alpha = 0.5) +
  ggrepel::geom_text_repel(aes(label = first), size = 3.5, max.overlaps = 10) +
  labs(x = "Points Scored per Game", y = "Points Against per Game",
       title = "Team points for vs. points against per game",
       subtitle = "Dashed lines represent league averages") +
  scale_x_continuous(breaks = seq(0, 200, by = 5)) +
  scale_y_continuous(breaks = seq(0, 200, by = 2.5))
```

### optimal lineup setting v2

```{r}
true_optimal_pts_weekly = espn_potentialpoints(conn, weeks = 1:max(end_games$week)) |>
  distinct(week, franchise_name, franchise_score) |>
  inner_join(espn_potentialpoints(conn, weeks = 1:max(end_games$week)) |>
  filter(!is.na(optimal_slot)) |>
  group_by(week, franchise_name) |>
  summarise(opt = sum(player_score),
            .groups = "drop"), by = c("week", "franchise_name")) |>
  setNames(c("week", "franchise_name", "true_score", "opt_score")) |>
  mutate(missed = round(opt_score - true_score, 2))

vis_data = true_optimal_pts_weekly |>
  filter(week == max(end_games$week)) |>
  inner_join(team_name_to_name, by = "franchise_name") |>
  arrange(missed) |>
  transmute(name = paste0(first, " (", missed, ")"),
            true_score, opt_score)

name_order = vis_data$name

vis_data |>
  mutate(name = factor(name, levels = rev(name_order))) |>
  pivot_longer(!name, names_to = "which", values_to = "pts") |>
  mutate(which = ifelse(which == "opt_score", "Optimal", "Actual")) |>
  ggplot(aes(name, pts)) +
  geom_col(aes(fill = which), position = "dodge") +
  geom_text(aes(label = pts), size = 3, hjust = -0.15, alpha = 0.5,
            position = position_dodge2(width = 0.9)) +
  coord_flip(ylim = c(0, max(vis_data$opt_score) * 1.05)) +
  labs(x = NULL, y = "Points Scored", fill = NULL,
       title = "Who sucked at setting their lineup this past week?",
       subtitle = "Top (best) to bottom (worst)") +
  scale_fill_manual(values = c("indianred3", "springgreen4")) +
  scale_y_continuous(breaks = seq(0, 250, by = 10))
```

### season long optimal lineups v2

```{r}
vis_data = true_optimal_pts_weekly |>
  inner_join(team_name_to_name, by = "franchise_name") |>
  group_by(franchise_name) |>
  summarise(true_score = sum(true_score),
            opt_score = sum(opt_score),
            missed = sum(missed)) |>
  inner_join(team_name_to_name, by = "franchise_name") |>
  arrange(missed) |>
  transmute(name = paste0(first, " (", missed, ")"),
            true_score, opt_score)

name_order = vis_data$name

vis_data |>
  mutate(name = factor(name, levels = rev(name_order))) |>
  pivot_longer(!name, names_to = "which", values_to = "pts") |>
  mutate(which = ifelse(which == "opt_score", "Optimal", "Actual")) |>
  ggplot(aes(name, pts)) +
  geom_col(aes(fill = which), position = "dodge") +
  geom_text(aes(label = pts), size = 3, hjust = -0.15, alpha = 0.5,
            position = position_dodge2(width = 0.9)) +
  coord_flip(ylim = c(0, max(vis_data$opt_score) * 1.05)) +
  labs(x = NULL, y = "Points Scored", fill = NULL,
       title = "Who has been the best at setting their lineup this season?",
       subtitle = "Top (best) to bottom (worst)") +
  scale_fill_manual(values = c("indianred3", "springgreen4"))
```

### most pts scored in a loss v2

```{r}
x = end_games |>
  slice_max(lose_score, n = 5, with_ties = F) |>
  inner_join(team_name_to_name, by = c("win_team" = "franchise_name")) |>
  rename(win_name = first) |>
  inner_join(team_name_to_name, by = c("lose_team" = "franchise_name")) |>
  rename(lose_name = first) |>
  mutate(score = paste0(win_score, "-", lose_score)) |>
  mutate(x = as.character(glue("Week {week}: {win_name} def. {lose_name} {score}"))) |>
  pull(x)
```

- `r x[1]`
- `r x[2]`
- `r x[3]`
- `r x[4]`
- `r x[5]`























### NEW STUFF

```{r}
true_proj_scores_weekly = ff_starters(conn, week = 1:max(end_games$week)) |>
  filter(!lineup_slot %in% c("BE", "IR")) |>
  group_by(week, franchise_name) |>
  summarise(true_score = mean(franchise_score),
            proj_score = round(sum(projected_score), 2),
            .groups = "drop")

end_with_proj = end_games |>
  inner_join(true_proj_scores_weekly, by = c("win_team" = "franchise_name", "week")) |>
  rename(win_proj_score = proj_score) |>
  inner_join(true_proj_scores_weekly, by = c("lose_team" = "franchise_name", "week")) |>
  rename(lose_proj_score = proj_score) |>
  select(!contains("true")) |>
  mutate(win_score_over_proj = win_score - win_proj_score,
         lose_score_over_proj = lose_score - lose_proj_score)

get_team_score_over_proj = function(tm) {
  w = end_with_proj |> filter(win_team == tm) |> pull(win_score_over_proj)
  l = end_with_proj |> filter(lose_team == tm) |> pull(lose_score_over_proj)
  return(sum(c(w, l)))
}

get_team_opp_score_over_proj = function(tm) {
  w = end_with_proj |> filter(win_team == tm) |> pull(lose_score_over_proj)
  l = end_with_proj |> filter(lose_team == tm) |> pull(win_score_over_proj)
  return(sum(c(w, l ) * -1))
}

names_logos = ffscrapr::ff_franchises(conn) |>
  distinct(franchise_name, logo)

data.frame(team = all_teams) |>
  mutate(sop = sapply(team, get_team_score_over_proj),
         luck = sapply(team, get_team_opp_score_over_proj),
         total = sop + luck) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  ggplot(aes(sop, luck)) +
  geom_point(aes(col = total), shape = "square", size = 4, show.legend = F) +
  ggrepel::geom_text_repel(aes(label = first), size = 3.5, max.overlaps = 10) +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(x = "Scoring Over Expected",
       y = "Opponent Scoring Under Expected",
       title = "Who is a ball knower and who is a luck merchant?") +
  scale_x_continuous(breaks = seq(-250, 250, by = 20)) +
  scale_y_continuous(breaks = seq(-250, 250, by = 20))
```


```{r}
library(ggimage)

names_logos = ff_franchises(conn) |>
  distinct(franchise_name, logo)

data.frame(team = all_teams) |>
  mutate(sop = sapply(team, get_team_score_over_proj),
         luck = sapply(team, get_team_opp_score_over_proj),
         total = sop + luck) |>
  inner_join(team_name_to_name, by = c("team" = "franchise_name")) |>
  inner_join(names_logos, by = c("team" = "franchise_name")) |>
  ggplot(aes(sop, luck)) +
  ggimage::geom_image(aes(image = logo), size = 0.2) +
  scale_color_gradient(low = "indianred3", high = "springgreen4") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(x = "Scoring Over Expected",
       y = "Opponent Scoring Under Expected",
       title = "Who is a ball knower and who is a luck merchant?") +
  scale_x_continuous(breaks = seq(-250, 250, by = 20)) +
  scale_y_continuous(breaks = seq(-250, 250, by = 20))
```

```{r}
get_opp_proj_scores = function(tm) {
  w = end_with_proj |> filter(win_team == tm) |> pull(lose_proj_score)
  l = end_with_proj |> filter(lose_team == tm) |> pull(win_proj_score)
  return(round(mean(c(w, l)), 2))
}

data.frame(team = all_teams) |>
  mutate(sos = sapply(team, get_opp_proj_scores)) |>
  inner_join(team_records, by = "team") |>
  ggplot(aes(sos, win_pct)) +
  geom_text(aes(label = first), size = 4) +
  geom_line(stat = "smooth", formula = y ~ x, method = "lm", linetype = "dashed")
```













































